intro

### 2021-11-05 06_Paper/ER-ED/intro.Rmd
corrected paragraph on SVs

<!-- Einführung ER -->
[...]
Implications of subjectively reported habitual use of emotion regulation strategies for affect and well-being have been discussed [@GrossJohn2003]. 
Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the assumption of *adaptive* and *maladaptive* strategies.
For example, it could be shown that maladaptive ER strategies mediate the effect between Neurotizism and depressive symptoms [@Yoon2013].
Also, meta-analytic evidence exists linking a number of ER strategies with psychological disorders [@Aldao2010].
The postulation of *adaptive* and *maladaptive* strategies was put in a new perspective with the concept of ER flexibility.
Similar to other psychological domains, e.g., attention and goal pursuit, *maladaptive* now refers to inflexible strategy use or use of strategies that are hindering in the achievement of goals [@Aldao2015].
First, adaptive flexible ER requires having a large repertoire of ER strategies [@Aldao2015]. 
For example, greater ER variability is related to reduced negative affect and therefore adaptive in daily life [@Blanke2020].
Second, strategies have to be chosen from the repertoire that are useful for goal achieving.
This selection of strategies is influenced by numerous factors.
For example, it was shown that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
Higher intensity of the stimulus leads to a choice of rather disengaging strategies, like distraction[@Sheppes2011;@Sheppes2014].
Further influencing factors are for example extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
Especially for effort, Scheffel and colleagues [-@Scheffel2021] could show that the choice for an ER strategy is mainly influenced by effort.
In this study, participants used the strategies distancing and suppression while inspecting emotional pictures.
Afterwards they could choose, which strategy they want to use again.
Participants tended to re-apply the strategy that was less effortful, even though it was not the most effective one.

[...]

What was missing in this research so far was the information regarding the strategy not chosen. 
People choose a strategy that they prefer, for whatever reason. 
However, nothing is revealed about the strategy that is not chosen.
On the one hand, it could be possible that the chosen strategy is the clear preference, the unchosen strategy is not a realistic option for the individual. 
On the other hand, it could also be that two strategies available for selection could represent almost equivalent options for the individual.
This leads to the question of how individual subjective values of ER strategies are characterized an how one can determine them. 
Individual subjective values (SV) of effortful tasks have been quantified using the cognitive effort discounting paradigm (COG-ED) [@Westbrook2013].

>>>>

<!-- Einführung ER -->
[...]
Implications of subjectively reported habitual use of emotion regulation strategies for affect and well-being have been discussed [@GrossJohn2003]. 
Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the assumption of *adaptive* and *maladaptive* strategies.
For example, it could be shown that maladaptive ER strategies mediate the effect between Neurotizism and depressive symptoms [@Yoon2013].
Also, meta-analytic evidence exists linking a number of ER strategies with psychological disorders [@Aldao2010].
The postulation of *adaptive* and *maladaptive* strategies was put in a new perspective with the concept of ER flexibility.
Similar to other psychological domains, e.g., attention and goal pursuit, *maladaptive* now refers to inflexible strategy use or use of strategies that are hindering in the achievement of goals [@Aldao2015].
First, adaptive flexible ER requires having a large repertoire of ER strategies [@Aldao2015]. 
For example, greater ER variability is related to reduced negative affect and therefore adaptive in daily life [@Blanke2020].
Second, strategies have to be chosen from the repertoire that are useful for goal achieving.
This selection of strategies is influenced by numerous factors.
For example, it was shown that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
Higher intensity of the stimulus leads to a choice of rather disengaging strategies, like distraction[@Sheppes2011;@Sheppes2014].
Further influencing factors are for example extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
Especially for effort, Scheffel and colleagues [-@Scheffel2021] could show that the choice for an ER strategy is mainly influenced by effort.
In this study, participants used the strategies distancing and suppression while inspecting emotional pictures.
Afterwards they could choose, which strategy they want to use again.
Participants tended to re-apply the strategy that was less effortful, even though it was not the most effective one - in this case: suppression.
Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.

However, what has been missing in research on ER choice so far is information regarding the strategy *not* chosen.
People choose a strategy that they prefer, for different, relatively well-known reasons. 
However, nothing is revealed about the strategy that is not chosen.
On the one hand, it could be possible that the chosen strategy represents the clear preference of an individual.
The strategy that was not chosen is not a realistic option for the individual. 
On the other hand, it could also be that two strategies available for selection could represent almost equivalent options for the individual.
To investigate this question, the individual subjective values of each strategy available for selection would have to be determined.
Promising approaches can be found in studies on difficulty levels of effortful cognitive tasks.  
Individual subjective values (SV) of effortful cognitive tasks have been quantified using the cognitive effort discounting paradigm (COG-ED) [@Westbrook2013].
